%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,letterpaper,palatine]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{textcomp}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.95]{geometry}
\usepackage{multicol}
\usepackage{import}

% personal data
\name{Tao Zhu}{}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{\faMapMarker\enspace  2636 Melfa Lane, Vancouver, BC,  V6T 2C6}
  
\newcommand*{\customcventry}[7][.10em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.10em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

  
\setlength{\tabcolsep}{12pt}
\renewcommand{\labelitemi}{\small$\bullet$}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-21mm}
\begin{center}
\faEnvelope{ zhutaosx@gmail.com }
\faHome{ \href{https://github.com/Legitao}{https://github.com/Legitao} }
\faMobile{ +1-236-988-1308 } \\
% \faGithub{ \href{https://github.com/Xiang-Gu}{Xiang-Gu} }
% \faLinkedin{ \href{https://www.linkedin.com/in/guxiang/}{guxiang} }
\end{center}

\vspace*{-7mm}
\section{EDUCATION}
\vspace*{-2mm}
{\customcventry{Sept. 2019 -- Dec. 2021 (Expected)}{M.Eng. in Computer Engineering}{The University of British Columbia}{Vancouver, BC}{}{GPA: 3.74/4.0}}
 
{\customcventry{Sep. 2015 -- Jun. 2019}{B.S. in Computer Science}{Shanghai Jiao Tong University}{Shanghai, China}{}{GPA: 3.7/4.0}}

\vspace*{-4mm}
\section{PROFESSIONAL EXPERIENCE}
\vspace*{-2mm}

\setlength{\parskip}{0.2em}
{\customcventry{Jun. 2020 -- Sept. 2020}{\textbf{Research Intern}}{Software AnaLysis and Testing (SALT) lab, UBC}{Vancouver, Canada}{}{}}
  {\begin{itemize}
    \item Performed an empirical study of using the Graph Neural Network(GNN) with PyTorch to automatically fix JavaScript bugs in a large dataset.
    \item Utilized Docker to containerize the GNN application to run on different servers.
  \end{itemize}
}

{\customcventry{Jun. 2018 -- Sept. 2018}{\textbf{Software Engineer Intern}}{Intel Corporation}{Shanghai, China}{}{}}
  {\begin{itemize}
    \item Developed database performance benchmark for Intel’s Zero-day Linux kernel performance testing framework using Shell and Ruby.
    \item Developed virtual machine testing functionality to automatically install and invoke the framework from hosting machine.
    \item Assisted in writing the documentation of the framework.
    \item URL:www.github.com/intel/lkp-tests
  \end{itemize}
}

\setlength{\parskip}{0.2em}

\vspace*{-4mm}
\section{SELECTED PROJECTS}
\vspace*{-2mm}

\customcvproject{Blockchain Donation Platform}{Jan. 2020 -- April. 2020}{Blockchain Software Engineering Course Project}
\begin{itemize}
    \item Developed a digital currency(Ether) donation platform as an decentralized application on the Ethereum blockchain using Truffle framework.
    \item Wrote smart contracts with the Solidity programming language. Tested the smart contracts using Mocha and deployed them to the local blockchain in Ganache.
    \item Built a dynamically rendered front end using React.js. Used Metamask extension to connect to our local Ethereum blockchain.
\end{itemize}

\customcvproject{Shopping Store Web Application}{Sept. 2019 -- Dec 2019}{Building Modern Web Applications Course Project}
\begin{itemize}
    \item Developed an online store web app with product filter and checkout functionality.
    \item Built a dynamically rendered front end with AJAX communication to the server.
    \item Designed a backend server with REST API using Node.js and Express.js and connected it to MongoDB.
\end{itemize}


\customcvproject{Robocode Learning System}{Sept. 2019 -- Dec 2019}{Architecture of Learning Systems Course Project}
\begin{itemize}
    \item Developed the controller of robocode tank with neural net and reinforcement learning using Java.
    \item Implemented the SARSA (on policy) version of the controller system and compared it with Q learning (off policy).
    \item Implemented a neural net to replace the look-up table and approximate Q function.
\end{itemize}

\customcvproject{Facial Expression Recognition System}{Oct. 2018 -- Feb. 2019}{}
\begin{itemize}
    \item Developed an end-to-end facial expression recognition system with convolutional neural network and support vector machine to classify facial expression using Python.
    \item Implemented functionality of image preprocessing, feature extraction and classification. The model reaches an accuracy of 95\%.
    \item Wrote a technical report summarizing the work.
\end{itemize}


{\customcvproject{Linux Kernel Enhancement Project}{Feb 2018 - Jul. 2018}{Operating System Course Project}}
\begin{itemize}
    \item Implemented a Linux system call to print the entire process tree in DFS order and another system call to translate the virtual address of a process to physical address.
    \item Changed Linux page replacement algorithm to second-chance algorithm.
\end{itemize}

% {\customcvproject{Data Structure}{Sep. 2017 -- Feb. 2018}{Data Structure Course Project}}
% \begin{itemize}
%     \item Programmed, debugged, tested in IntelliJ with Java.
%     \item Improved skills necessary for unit test with JUnit.
%     \item Implemented various core data structures (list, disjoint set, tree/hash set, tree/hash map, heap-based priority queue) and several classic algorithms on tree/graph traversal, shortest path, minimal spanning tree, compression and sorting. 
% \end{itemize}
% \vspace*{-4mm}
% \section{HONORS \& AWARDS}
% \vspace*{-2mm}
% \begin{minipage}{\maincolumnwidth}%
%     	\begin{itemize}
%           \item Outstanding Graduated Award (Awarded to $\leq$ 15\% graduated bachelors) \hfill {\itshape May 2019}
%         %   \item Department of Defense Scholarship \hfill {\itshape Jun. 2017}
%           \item Yang Yuanqing Educational Fund in Computer Science (\textyen 25,000) \hfill {\itshape Mar. 2017}
%         %   \item University Merit Student (Awarded to $\leq$ 3\% students each year) \hfill {\itshape Nov. 2016}
%         %   \item Outstanding Service Medal (Awarded from People's Liberation Army) \hfill {\itshape Sep. 2016}
% 		\end{itemize}%
% \end{minipage}%

\vspace*{-4mm}
\section{ADDITIONAL INFORMATION}
\vspace*{-2mm}
    \begin{itemize}
        \item Programming Languages: JavaScript, Python, Java, Python, JavaScript, C, C++, 
        \item Tools: Linux, Docker, Version Control (Git,  Github),Web Frameworks (React.js, Express.js, Node.js), Database(MongoDB),Testing ( JUnit), Communication ( \LaTeX), ,  Deep learning framework (Keras, PyTorch)
        \item Languages: Fluent in Chinese (first language) and English (TOEFL 109, GRE 331 + 4.0)
        % \item Work Eligibility: Eligible to work in Canada; will not require visa sponsorship for full-time employment
    \end{itemize}


      

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------
\end{CJK*}
\end{document}


%% end of file `template.tex'.

